---
title: "textmining_sentence_level"
author: "Shuting"
date: "12/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sentimentr)
library(ggplot2)
library(knitr)
```

## Import book by using tnum package

```{r}
#devtools::install_github("Truenumbers/tnum/tnum")
tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")
source("Book2TN-v6A-1.R")
#Metamorphosis_text <- readLines("Metamorphosis.txt")
Metamorphosis <- gutenberg_download(gutenberg_id = 5200)
Metamorphosis <- read.table("Metamorphosis.txt", header = T)

tnBooksFromLines(Metamorphosis$text, "Kafka/Metamorphosis")
tnum.getDBPathList(taxonomy = "subject", levels = 2)

Metamorphosis_txt <- tnum.query("Kafka/Metamorphosis# has text", max = 3000)
Metamorphosis_txt_df <- tnum.objectsToDf(Metamorphosis_txt)
```

## Do sentimentr on sentence

```{r}
sentiment=sentiment_by(get_sentences(Metamorphosis_txt_df$string.value))
summary(sentiment$ave_sentiment)

qplot(sentiment$ave_sentiment,geom="histogram",binwidth=0.1,main="Review Sentiment Histogram")

### add sentiment score to original data frame
Metamorphosis_txt_df$ave_sentiment=sentiment$ave_sentiment
Metamorphosis_txt_df$sd_sentiment=sentiment$sd

```
From the summary of sentiment score, reviews keep neutral in this book, but there are some extreme outliers, with the most positive review being 1.41 and the most negative being -1.45. We should remove them for further analysis.

## Recall the bag of words analysis

```{r,warning=FALSE,message=FALSE}
source(knitr::purl("textmining_ShutingLi.Rmd", quiet=TRUE))

tidy_Metamorphosis_line <- tidy_Metamorphosis %>%
  inner_join(get_sentiments("afinn")) %>% 
  group_by(linenumber) %>% 
  summarise(sentiment = sum(value), n=n())

tidy_Metamorphosis_line$ave_sentiment <- tidy_Metamorphosis_line$sentiment/tidy_Metamorphosis_line$n

ggplot(tidy_Metamorphosis_line, aes(linenumber, ave_sentiment, fill=factor(linenumber))) +
  geom_col(show.legend = FALSE)
```
I use the sentiment value we get from the bag of words analysis based on dictionary "afinn" as the sentiment score, and aggregate them by line number, then I get the sentiment score at line level.

Here is the plot to show the sentiment trendency on line level.


## Compare the result from the sentimentr 

```{r}
Metamorphosis_txt_df <- Metamorphosis_txt_df %>% mutate(linenumber = row_number())
ggplot(Metamorphosis_txt_df, aes(linenumber, ave_sentiment, fill=factor(linenumber))) +
  geom_col(show.legend = FALSE)
```
Here is the plot to show the sentiment trendency based on sentimentr analysis.


